Subtle Gestures with the J!NS MEME

### 2021-08-05 Paper/paper.tex
Collect some Related Work

% Assigned to FB
\section{Related Work}
Something about subtlety \cite{10.1145/3290605.3300648}. Then something
about other research involving the J!NS MEME \cite{10.1145/3123021.3123060}.
Then something about their tool for automating personalization
\cite{10.1145/3174910.3174953}.

>>>>

% As a reference, maybe useful later
Current smartglasses:
Smartglasses with cameras: Spectacles by Snap Inc. https://www.spectacles.com/
Smartglasses with EOG sensors: J!ns Meme by J!ns (website currently only in Japanese): https://jins-meme.com/

% Assigned to FB
\section{Related Work}
[Insert an introduction here]

[TODO More related work from KissGlass]

[TODO proper citations]
\subsection{Wearables with EOG sensors}
Bulling, A., Roggen, D., and Tröster, G. Wearable eog goggles: Eye-based interaction in everyday environments. CHI EA (2009).
\cite{10.1145/3123021.3123060}.
\subsection{Face Interaction}
EOG attached to in-ear head phones: Manabe, H., Fukumoto, M., and Yagi, T. Conductive rubber electrodes for earphone-based eye gesture input interface. PUC (Jan. 2015).
Harrison, C., Tan, D., and Morris, D. Skinput: Appropriating the body as an input surface. CHI (2010).
Serrano, M., Ens, B. M., and Irani, P. P. Exploring the use of hand-to-face input for interacting with head-worn displays. CHI (2014).
Lissermann, R., Huber, J., Hadjakos, A., and Mühlhäuser, M. Earput: Augmenting behind-the-eardevices for ear-based interaction. CHI EA (2013).
Ashbrook, D., Tejada, C., Mehta, D., Jiminez, A.,Muralitharam, G., Gajendra, S., and Tallents, R. Bitey: An exploration of tooth click gestures for hands-free user interface control. MobileHCI (2016)
Jota, R., and Wigdor, D. Palpebrae superioris: Exploring the design space of eyelid gestures. GI (2015).
Apple Watch Users Discover Another Way to Go ‘Hands Free’. https://www.wsj.com/articles/nosy-apple-watch-users-discover-another-way-to-go-hands-free-1451077454.
\subsection{Recognition with Smartglasses}
Ishimaru, S., Kunze, K., Uema, Y., Kise, K., Inami, M.,and Tanaka, K. Smarter eyewear: Using commercial eog glasses for activity recognition. UbiComp Adj. (2014).
KissGlass: https://dl.acm.org/doi/10.1145/3384657.3384801
Then something about their tool for automating personalization \cite{10.1145/3174910.3174953}.
Something about subtlety \cite{10.1145/3290605.3300648}.
